Limited physiological plasticity and reduced relative variance in physiological rates of ectotherm populations under climate change

### 2024-07-12 ms.qmd
Testing out rate variation for sims, but don't make a difference

#parameters
set.seed(23)
 delta_ind_sd = seq(0.01, 2, by =0.20)
 alpha_ind_sd = 0.05
 sigma_ind_sd = seq(0.01, 2, by =0.20)
        delta =  35 
        sigma =  9  
        alpha = -15
            n = 1000

# create all combuinations of sd
sims <- expand.grid(delta_ind_sd, alpha_ind_sd, sigma_ind_sd) %>% 
  mutate(sim = row_number())  %>% rename(delta = Var1, alpha = Var2, sigma = Var3)

@@

@@

lncvr_sim_delta_sigma <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnCVR)) +
  geom_contour_filled(bins = bins_cvr) +
  scale_color_viridis(direction = -1) +
  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
       fill = TeX("$lnCVR_{Q_{10}}$")) + theme_classic()+ my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))

lnvr_sim_delta_sigma <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnVR)) +
  geom_contour_filled(bins = bins_vr) +
  scale_color_viridis() +
  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
       fill = TeX("$lnVR_{Q_{10}}$")) + theme_classic() + my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))

p_sim2 <- (lncvr_sim_delta_sigma + lnvr_sim_delta_sigma) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
p_sim2
```

>>>>

@@

#parameters
  set.seed(23)
 delta_ind_sd = seq(0.01, 2, by = 0.20)
 alpha_ind_sd = 0.01
 sigma_ind_sd = seq(0.01, 2, by = 0.20)
        delta =  35 
        sigma =  9  
        alpha = -15 
            n = 1000
            z = seq(0,45,0.1) # Temperature gradient

# create all combinations of sd
sims <- expand.grid(delta_ind_sd, alpha_ind_sd, sigma_ind_sd) %>% 
  mutate(sim = row_number())  %>% rename(delta = Var1, alpha = Var2, sigma = Var3)

@@

lncvr_sim_delta_sigma1 <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnCVR)) +
  geom_contour_filled(bins = bins_cvr) +
  scale_color_viridis(direction = -1) +
  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
       fill = TeX("$lnCVR_{Q_{10}}$"), title = TeX("Variation in Rates ($\\sigma_{\\alpha}$ = 0.01)")) + theme_classic()+ my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))

lnvr_sim_delta_sigma1 <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnVR)) +
  geom_contour_filled(bins = bins_vr) +
  scale_color_viridis() +
  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
       fill = TeX("$lnVR_{Q_{10}}$")) + theme_classic() + my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))

p_sim2 <- ((lncvr_sim_delta_sigma1 + lnvr_sim_delta_sigma1)) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
ggsave(p_sim2, width = 20, height = 10, filename = "./output/figures/figS13_new.pdf")

p_sim2 <- image_read("./output/figures/figS13.pdf")
p_sim2
```

```{r}
#| label: sim3
#| echo: false
#| include: false

# Simulation 1. Assume optimum is rather constant among individuals 
#parameters
delta =  35 + rnorm(n,0,5) 
sigma =  20 +rnorm(n,0,0.1)
alpha = 0.0001 +rnorm(n,0,1)

ws1<- list()
for(i in 1:length(delta)){
ws1[[i]] <- 2*exp(-(z-delta[i])^2/(2*sigma[i]^2))*pnorm(alpha[i]*(z-delta[i])/sigma[i])
}

# mean, SD and CV
  sum_sim4 <- ws1 %>% 
              filter(z %in% c(18, 28)) %>% 
              group_by(z) %>% 
              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())

ggplot(ws1, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim4, 10)

#---------
# Parameters
# temp temperature in degrees centigrade
# r_tref rate at the standardised temperature, tref
# e activation energy (eV)
# el low temperature de-activation energy (eV)
# tl temperature (ºC) at which enzyme is 1/2 active and 1/2 suppressed due to low temperatures
# eh high temperature de-activation energy (eV)
# th temperature (ºC) at which enzyme is 1/2 active and 1/2 suppressed due to high temperatures
# tref standardisation temperature in degrees centigrade. Temperature at which rates are not inactivated by either high or low temperatures

eh <- 1
el <- 0.2
tl <- 5
th <- 40
tref <- 20
r_tref <- 1
e <- 0.65
temp <- seq(0, 60, 0.1)

# Sharpe-Schoolfield Arrhenius equation
sharpeschoolfull_1981 <- function(temp, r_tref, e, el, tl, eh, th, tref){
  tref <- 273.15 + tref
  k <- 8.62e-05
  boltzmann.term <- r_tref*exp(e/k * (1/tref - 1/(temp + 273.15)))
  inactivation.term <- 1/(1 + exp(-el/k * (1/(tl + 273.15) - 1/(temp + 273.15))) + exp(eh/k * (1/(th + 273.15) - 1/(temp + 273.15))))
  return(boltzmann.term * inactivation.term)
}

per <- sharpeschoolfull_1981(temp, r_tref, e, el, tl, eh, th, tref)

# Create a data frame for plotting
df <- data.frame(Temperature = temp, Rate = per)

ggplot(df, aes(x = Temperature, y = Rate)) +
  geom_line(color = "blue") +
  theme_minimal() +
  labs(title = "Sharpe-Schoolfield Arrhenius Equation",
       x = "Temperature (K)",
       y = "Rate")

#------

#T body temp,(Ta)
#QT, temperature coefficient
#C, constant in shifts of vertical axis
#Tth, temperature of thermal threshold
#d, constant in shifts of horizontal axis

pf <- function(T, Tthres, d, C, QT){
  therm <- C*exp((T*log10(QT))/10)
      d <- ifelse(T<Tthres, 1, (1-d*(Tthres - T)^2))
 return(therm*d)
}

T = seq(5, 50, 0.1)
Tthres = 25
d = 0.01
C = 0.1
QT = 4

pf1 <- c()
for(i in 1:length(T)){
  pf1[i] <- pf(T[i], Tthres, d, C, QT)
}
plot(T, pf1, type = "l", xlab = "Temperature", ylab = "Performance", main = "Performance Curve")
